MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
added some codes for defender proximity analysis (correlate between defender distance with points made)

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis  
c. Shot Clock Pressure  
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage  
h. Fatigue Effect (Number of Rest Day)  
i.

@@

>>>>

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis (Reza)
c. Shot Clock Pressure  
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage  
h. Fatigue Effect (Number of Rest Day)  
i.

@@

###Defender Proximity Analysis
```{r}
#Data Preparation
#Change the value of shot result column to numeric
df[, "SHOT_RESULT"] <- as.character(df[, "SHOT_RESULT"])
for (j in 1:nrow(df)){
  df[j, "SHOT_RESULT"] <- ifelse (df[j, "SHOT_RESULT"] == "made", 1, 0)
}

#set the value to numeric
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[, "PTS_TYPE"] <- as.integer(df[, "PTS_TYPE"])
df[, "CLOSE_DEF_DIS"] <- as.numeric(df[, "CLOSE_DEF_DIST"])

#calculate correlation between defender distance and shot result
cor(df[, "SHOT_RESULT"], df[, "CLOSE_DEF_DIS"])

#calculate correlation between defender distance and points made (2 or 3 points)
cor(df[, "PTS_TYPE"], df[, "CLOSE_DEF_DIS"])

#plot the diagram
library(ggplot2)
ggplot(data = df, aes(x = PTS_TYPE, y = CLOSE_DEF_DIST, group = PTS_TYPE)) + geom_boxplot() + stat_summary(fun.y = mean, geom = "point", shape = 5, size = 1) +ggtitle("Points Scored based on Distance from Defender")
```
